\documentclass{article}


\usepackage{arxiv}

\usepackage[utf8]{luainputenc}	% allow utf-8 input with LuaLaTeX
\usepackage[T1]{fontenc}    	% use 8-bit T1 fonts
\usepackage{palatino}			% use palatino font
\usepackage{hyperref}       	% hyperlinks
\usepackage{url}            	% simple URL typesetting
\usepackage{booktabs}       	% professional-quality tables
\usepackage{amsfonts}       	% blackboard math symbols
\usepackage{amsthm}
\usepackage{nicefrac}       	% compact symbols for 1/2, etc.
\usepackage{microtype}      	% microtypography
\usepackage{amsmath}
\usepackage[compat=1.1.0]{tikz-feynman}
\usepackage{tikz}
\usepackage{slashed}
\usepackage{mathtools}
\usepackage{dsfont}
\usepackage{geometry}
\usepackage{caption}
\usepackage[onehalfspacing]{setspace}
\usepackage{titlesec}
\usepackage[stable]{footmisc}	% suppress footnotes in table of contents

% fix wrong title spacing induced by onehalfspacing from setspace package
\titlespacing*{\section}
{0pt}{0ex}{0ex}
\titlespacing*{\subsection}
{0pt}{0ex}{0ex}
\titlespacing*{\subsubsection}
{0pt}{0ex}{0ex}

% define tick
\def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;}  


\numberwithin{equation}{section} % numbers equations by section

\newcommand{\Tr}{\mathrm{Tr}}
\newcommand{\wtilde}{\widetilde}
\newcommand{\fsl}{\slashed}
\newcommand{\lbr}{\left\lbrace}
\newcommand{\rbr}{\right\rbrace}
\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
            \node[shape=circle,draw,inner sep=0.5pt] (char) {#1};}}
\newcommand{\numberthis}{\addtocounter{equation}{1}\tag{\theequation}} % number equation in unnumbered align/equation environment
\newcommand{\numberitem}{\hfill\refstepcounter{equation}\textup{(\theequation)}}




\title{Contribution of QED to Rational Terms in 1-loop Feynman Diagrams in the Standard Model}


\author{
  Jonathan Kley \\
  Department of Physics\\
  Technical University of Munich\\
  James-Franck-Str. 1, 85748 Garching \\
  \texttt{jonathan.kley@tum.de} \\
}

\begin{document}

\maketitle

\begin{abstract}
For years it has been of high interest to automate the calculation of Feynman diagrams in the Standard Model (SM) in order to be able to keep up with the increasing precision of experimental data. A lot of efforts have been made in the early 2000s to make progress in this direction where one of the big milestones was the proof that any amplitude in the SM can be decomposed into a box-, a triangle-, a bubble-, a tadpole-subdiagram and a rational term which can be of two types. In this paper we investigate the $\epsilon$-dimensional contribution of dimensional regularisation to this rational term. If all of the coefficients in the composition into the mentioned subdiagrams alongside the rational terms are known we obtain an effective treelike theory giving us 1-loop results for the whole SM. \\
This paper is structured as follows: After a short introduction to the subject, we first calculate $R_2$ in pure QED as a warm-up and then the QED contribution to $R_2$ in the SM. Then, we renormalize QED in terms of scalar integrals and calculate the contribution of QED to the renormalization of the SM. Once this is done, we are able to implement an algorithm to automate calculations in the SM and can compare our results to the results from other references.\end{abstract}


% keywords can be removed
\keywords{QFT \and 1-loop Feynman Diagrams \and Rational Terms \and More}

\newpage
\tableofcontents
\newpage

\include{Sections/Introduction}
\include{Sections/pureQED}
\include{Sections/QED2SM}
\include{Sections/Renormalization}
\include{Sections/Appendices}


\bibliographystyle{unsrt}  
\bibliography{references}


\end{document}
